### 2022-05-18 main/chapter_2ljets.tex
clear up chapter start

% begin with physics content and results
My main result in this thesis is displayed in Figure~\ref{fig:2ljets_summary}.

It shows unblinded regions from the electroweak part of
Reference~\cite{atlas2022searches}, which reports searches
``for new phenomena in events with two leptons, jets, and missing
transverse momentum''.
For brevity, I will name that search $\twoljets$.

This section begins with a splash summary of interpretations of the results in
Figure~\ref{fig:2ljets_summary},
before cutting through the gory details later on.

In a large number orthogonal signal regions, where non-standard signals would
encourage excess data above backgrounds,
no significant excess is observed above \emph{post-fit} background expectations.
Indeed there are some significant deficits --- data below the background noise.

@@

\FloatBarrier
\subsection{Contributions}
My contributions the the analysis are listed here.
\begin{itemize}
\item Design, implementation and execution of the electroweak part of the analysis.
\item Service as `analysis contact' from January to October 2020.
\item Production of main data inputs for all three analyses
and the RJR $3\ell$ search \TODO{cite}.
Production of all systematic variations for the background samples;
other group members assisted with the central background sample.
Production of all electroweak signal samples and their systematic variations.
\item Integration with ATLAS combinations and pMSSM scan efforts by
performing their validation studies and serializing the analysis results.
\item Preparation of electroweak results for publication in the paper \TODO{cite} and the
public HEPData record~\cite{maguire2017hepdata}.
\end{itemize}
Except where specified, I produced all figures presented in this thesis.
Many plotting scripts, however, are modified from versions inherited from
many \atlas\ members past and present to whom I am grateful.

@@

\clearpage
\FloatBarrier
\section{Origins}
% previous results on 2(/3)L from ATLAS
% other constraints on these models from ATLAS/CMS
% previous region design, motivation for this work
Previous analyses of \atlas\ data have explored similar selections of
two leptons, jets, and missing transverse momentum.
Quite a few analyses, in fact.
This project exists to supplement those results with information from the full
LHC Run 2 data-set which was completed in 2018 and contains
$139~\mathrm{fb}^{-1}$ of usable proton-proton collisions at $\sqrt{s} = 13~\eV[T]$.
Leverage of the increased data quantity is one key aim.
Analysis quality also might be improved if our designs can take lessons from
the experiences of previous work.

@@

The $\twoljets$ analysis is a trinity,
of which all three parts expand upon \atlas\ results which previously appeared
in separate publications.
These three parts are named `RJR', `electroweak', and `strong', each of which
is described in its historical context in this section.

@@

My primary contributions are to the $\twoljets$ electroweak analysis,
detailed in Section~\ref{sec:2ljets_origins_electroweak},
which uses conventional (non-RJR) event variables to define a collection of
orthogonal regions in a search for effects from the electroweak sector of
supersymmetric models.

@@

\paragraph{RJR versus conventional}
Disappearing excesses have encouraged doubts about RJR variables;
the existence of the `RJR-mimic' paper~\cite{atlas_rjr_mimic_SUSY_2018_06}
is public evidence of this.

>>>>

We begin with a quick summary of results from my work on this search project;
the coming section briefly presents the plots and tables which I personally
find first when looking at an \atlas\ search paper.
The the meat of this chapter (or if you prefer, its gory details) follows in
Section~\ref{sec:2ljets_context} onwards.

\subsection{Splash summary}

% begin with physics content and results
The sum of my work presented in this thesis is displayed in
Figure~\ref{fig:2ljets_summary}.
It illustrated the unblinded results in regions of the electroweak part of the
recent \atlas\ search ``for new phenomena in events with two leptons, jets, and
missing transverse momentum''~\cite{atlas2022searches}.
For brevity, I call this search $\twoljets$.

In a large number orthogonal signal regions, no significant excess is observed
above \emph{post-fit} backgrounds.
Indeed there are some significant deficits --- data below the background noise.

@@

\FloatBarrier
\subsection{Contributions}

This subsection claims attributions of work on the $\twoljets$ analysis.

\begin{itemize}
\item Design, implementation and execution of the electroweak part of the analysis.
\item Service as `analysis contact' from January to October 2020.
\item Production of main data inputs for all three analyses
and the RJR $3\ell$ search \TODO{cite}.
Production of all systematic variations for the background samples;
other group members assisted with the central background sample.
Production of all electroweak signal samples and their systematic variations.
\item Integration with ATLAS combinations and pMSSM scan efforts by
performing their validation studies and serializing the analysis results.
\item Preparation of electroweak results for publication in the paper \TODO{cite} and the
public HEPData record~\cite{maguire2017hepdata}.
\end{itemize}
Except where specified, I produced all figures presented in this thesis.
Many plotting scripts, however, are modified from versions inherited from
many \atlas\ members past and present to whom I am grateful.

@@

\clearpage
\FloatBarrier
\section{Context}
\label{sec:2ljets_context}
% previous results on 2(/3)L from ATLAS
% other constraints on these models from ATLAS/CMS
% previous region design, motivation for this work
Previous analyses of \atlas\ data have explored similar selections of
two leptons, jets, and missing transverse momentum.
Quite a few analyses, in fact.
This project exists to supplement those results with information from the full
LHC Run 2 data-set which was completed in 2018 and contains
$139~\mathrm{fb}^{-1}$ of usable proton-proton collisions at $\sqrt{s} = 13~\eV[T]$.
Leverage of the increased data quantity is one key aim.
Analysis quality also might be improved if our designs can take lessons from
the experiences of previous work.

@@

The $\twoljets$ analysis is a trinity,
of which all three parts update previously published \atlas\ results.
These three parts are named `RJR', `electroweak', and `strong', each of which
is described in its historical context in this section.

@@

My primary contributions are to the $\twoljets$ electroweak analysis,
detailed in Section~\ref{sec:2ljets_origins_electroweak},
which uses conventional (non-RJR) event variables to define a collection of
orthogonal regions, and performs a search for effects from the electroweak
sectors of supersymmetric models.

@@

\paragraph{Versus conventional}
Disappearing excesses have encouraged doubts about RJR variables;
the existence of the `RJR-mimic' paper~\cite{atlas_rjr_mimic_SUSY_2018_06}
is public evidence of this.
